%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Oscar García Giménez CV
% o.garcia.gimenezgmail.com
% https://github.com/ogagi
%
% This template has been taken from
% http://www.latextemplates.com/template/classicthesis-styled-cv
% and odified by me to fit my needs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}
\reversemarginpar % Move the margin to the left of the page

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{NavyBlue}}

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=NavyBlue, linkcolor=NavyBlue} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Oscar Garc\'ia Gim\'enez}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{}{\textit{Born in Barcelona,}}{16 November 1983} % Birthplace and date

\NewEntry{email}{\href{mailto:oscar@oskarizu.net}{oscar@oskarizu.net}} % Email address

\NewEntry{website}{\href{http://okarizu.net}{http://oskarizu.net}} % Personal website

\NewEntry{phone}{(H) +34 (93) 172 39 60\ \ $\cdotp$\ \ (M) +34 667 630 202} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{2021--Present}{Senior Engineering Manager, \textsc{Bitpanda}  --- Barcelona}

\Description{\MarginText{Bitpanda} Currently managing 4 teams in the Product area of Onboarding and Marketing technologies, responsible of hiring and growing the teams within the Barcelona Tech HUB. Tech stack is PHP, Java, Golang and Angular, Swift and Kotlin for client applciations. Extracting
domain based services away from the current monolith and ensuring the scalability and relialability of the systems. In charge of 4 teams of approaximately 7-8 members each.}

\NewEntry{2020--2021}{Principal Software Engineer (Logistics), \textsc{Inditex}  --- Barcelona}

\Description{\MarginText{Inditex} In charge of the digital transformation of the Logistics branch of INDITEX with the main goal of moving the infrastucture of the platform from an "on premise" infractucture to a Cloud Native approach. Tech stack was Java application and custom libraries
developed in-house. Infrastucture runs on top of Microsoft Azure Cloud and the migration consisted in a 2 step phase first moving all the infra/platform to a K8s cluster in Red hat Openshift cluster and after consolidation of the process move to the Azure Cloud. In charge of 2 teams of approximately 8-10 
members each.}

\NewEntry{2019--2020}{Lead Software Developer, \textsc{Dow Jones}  --- Barcelona, Remote}

\Description{\MarginText{Dow Jones} Lead Software Developer in charge of the Data Pipelines to process the historical archive of news from TWSJ (The Wall street Journal) that serves several of the REST APIs provided by
the Dow Jones DNA initiative. Tech stack is scala, python and Angular for client applications everything running in Google Cloud Computing.}

\NewEntry{2019--2020}{Lead Platform Engineer, \textsc{Stuart Delivery}  --- Barcelona, Remote}

\Description{\MarginText{Stuart Delivery} Working on the Platform Team in the area of Spatial Technologies. Leading and growing the team from 4 Engineers to 14 Engineers and responsible of Architectural decisions as well as Roadmap definition for technical tasks.
Tech stack is scala, python (for Data Science related tasks) and Ruby on Rails for API based services.}

\NewEntry{2019--2020}{Senior Data Engineer, \textsc{Stuart Delivery}  --- Barcelona}

\Description{\MarginText{Stuart Delivery} Joined as Senior Data Engineer to work in the Spatial area of Stuart Tech. In charge of the service that provides the platform the functionality of Rider/Package assignment. Originally the service was built following a monolithic approach and presented some issues realted to
scalability and performance. Designed a plan to split the service in several micro-services that were able to scale. Tech stack is scala, python and Ruby on Rails and communication between services was powered by Kafka.}

\NewEntry{2015--2018}{Data Engineer, \textsc{XING Networking}  --- Barcelona}

\Description{\MarginText{XING Networking - Spain} Joined the Data Engineering, making the switch from QA Engineering to Software Development in the area of Data Engineering. Worked in the Search Engine of the platform driven by an Elasticsearch cluster and several services that provided indexing capabilities (near real time) and a service provinding a DSL to interact with the Elasticsearch cluster. \\ \href{https://www.xing.com}{https://www.xing.com}}

\NewEntry{2014--2015}{Senior Software Test Engineer, \textsc{XING Networking}  --- Barcelona}

\Description{\MarginText{XING Networking - Spain} As a Software Test Engineer I'm in charge of designing, mantaining and performing all related tasks to Testing in the project I'm working on. We are using Ruby on Rails as a backend framework and Backbone-Marionette as a main Front-end framework. The testing is done both manually and automatically using Jenkins as a CI. The Frameworks used for testing in our project are: RSpec, Capybara and Jasmine for the Javascript test suite.\\ \href{https://www.xing.com}{https://www.xing.com}}
%------------------------------------------------

\NewEntry{2013--2014}{Software Test Engineer, \textsc{XING Networking}  --- Barcelona}

\Description{\MarginText{XING Networking - Spain}.As a Software Test Engineer I'm in charge of designing, mantaining and performing all related tasks to Testing in the project I'm working on. We are using Ruby on Rails as a backend framework and Backbone-Marionette as a main Front-end framework. The testing is done both manually and automatically using Jenkins as a CI. The Frameworks used for testing in our project are: RSpec, Capybara and Jasmine for the Javascript test suite.\\ \href{https://www.xing.com}{https://www.xing.com}}
%------------------------------------------------

\NewEntry{2012--2013}{Senior QA Engineer, \textsc{Wuaki.tv}  --- Barcelona}

\Description{\MarginText{Wuaki.tv}VOD service on-line available in multiple devices. As a QA Engineer I'm in charge of developing and maintaining the automated test suite built with RSpec and Capybara for the Web Site and in Jasmine for the TV devices. One of our main goals has been to improve the execution time of our test suite by reducing it almost a 30\% . Another task our dept. has done is to improve and increase the release frequency (from once per month to twice per week) through the usage of different environments where to test the isolated feature, without the concerns of an integration environment, in that way we can ensure the value of the feature and let the integration tests do their job.\\ \href{http://es.wuaki.tv}{https://es.wuaki.tv}}
%------------------------------------------------

\NewEntry{2011--2012}{QA Engineer, \textsc{Kinamik Data Integrity S.L}  --- Barcelona}

\Description{\MarginText{Kinamik Data Integrity S.L}Working as a QA Engineer and a 3/4 Tier Support Engineer. Designing and Maintaining Test Plans/Suites, executing these test plans and providing support to our customers. Worked with Java and JBoss, and HSM technologies as well.}
%------------------------------------------------

\NewEntry{2010 -- 2011}{Technical Manager, \textsc{Avery Berkel ESP} --- Barcelona}

\Description{\MarginText{Avery Berkel Spain}Leading the technical team for Spain and Portugal. I've worked for almost 6 months in Birmingham, where the company HQ were placed, providing support and developing integration projects with our customers. \href{http://www.averyberkel.com/}{http://www.averyberkel.com/}}
%------------------------------------------------


\NewEntry{2009 -- 2010}{Post-Sales Agent, \textsc{ThinkSmart S.L} --- Barcelona}

\Description{\MarginText{ThinkSmart S.L}Developing the Post-sales department for Samsung in the area of Catalonia, dealing with customer issues and scheduling the deliver and fix dates. \href{http://www.thinksmart.es/}{http://www.thinksmart.es/}}
%------------------------------------------------


\NewEntry{2007 -- 2009}{Support Services Agent, \textsc{Krontime S.L} --- Barcelona}

\Description{\MarginText{Krontime S.L}Providing 1st and 2nd level support to customers and performing the on-site or remote installations of our products. Worked with VB6, HTML and JavaScript. \href{http://krontime.com/es}{http://krontime.com/es/}}
%------------------------------------------------

\vspace{1em} % Extra space between major sections
\newpage
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2006-2007}{CIPSA S.A, Barcelona}

\Description{\MarginText{IT Technician} UNIX/Linux Systems Administrator, Network Administration and Network Security.}

%------------------------------------------------

\NewEntry{2002-2007}{Universitat de Barcelona (UB), Barcelona}

\Description{\MarginText{Physics} }

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Computer Skills}\vspace{1em}

\Description{\MarginText{Languages}\textsc{java}, \textsc{ruby}, \textsc{scala}, \textsc{python}, \textsc{javascript}, \textsc{rust}}

\Description{\MarginText{Frameworks}\textsc{Rails}, \textsc{Sinatra}, \textsc{Spring}, \textsc{Play}, \textsc{ZIO}}

\Description{\MarginText{Testing Frameworks}\textsc{Capybara}, \textsc{RSpec}, \textsc{Cucumber}, \textsc{Jasmine}, \textsc{CalabashIOS}, \textsc{Appium}, \textsc{Kif}}

\Description{\MarginText{Databases}\textsc{MySQL}, \textsc{Redis}, \textsc{Elasticsearch}, \textsc{MongoDB}}

\Description{\MarginText{OS}\textsc{Mac OSX}, \textsc{Linux}, \textsc{Windows}}

\Description{\MarginText{Source Control}\textsc{git}, \textsc{SVN}}

\Description{\MarginText{Editors}\textsc{emacs}}

\Description{\MarginText{Text Formatting}\LaTeX, \textsc{MarkDown}, \textsc{Office}, \textsc{asciidoc}}

\Description{\MarginText{Infra}\LaTeX, \textsc{AWS}, \textsc{Google Cloud Computing}, \textsc{Azure}}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

\spacedlowsmallcaps{Additional information}\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Fluent}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{Spanish}}\ \ $\cdotp$\ \ \ Mother tongue}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{Catalan}}\ \ $\cdotp$\ \ \ Mother tongue}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{French}}\ \ $\cdotp$\ \ \ Only read and low level spoken}
%------------------------------------------------

\Description{\MarginText{Interests}Electric Guitar\ \ $\cdotp$\ \ Climbing\ \ $\cdotp$\ \ Running\ \ $\cdotp$\ \ Reading\ \ $\cdotp$\ \ Learning}

\vspace{1em} % Extra space between major sections

\spacedlowsmallcaps{References and links}\vspace{1em}

\Description{\MarginText{LinkedIn}In my LinkedIn profile are available the recommendations that my former employees and coleagues have written about me. \href{http://lnkd.in/iRQSep}{LinkedIN Profile - http://lnkd.in/iRQSep}}

\Description{\MarginText{Github}In my Github page you'll be able to find pieces of the work I've done with some of the programming languages I've learned during my career and the source of this cv. \href{http://github.com/okarizu}{http://github.com/oskarizu}}



%----------------------------------------------------------------------------------------

\vspace{10em} % Extra space between major sections

\end{cv}
This document has been written using \LaTeX and AUCTeX for emacs.
\end{document}
